My Days at the Home of the Merlin Engine

### 2013-07-18 pnsac/jul13/article_Feature1.tex
Final content for July 2013 newsletter.

@@

The UK being a small country, everybody went around by train.  As
usual, I was given very little information and told to get myself to
East Midlands airport early on the appointed morning, where a ticket
would be waiting for me. On this occasion I had the good sense to take
my own car to the airport and did not get lost. I expected to find a
plane waiting, painted in some sort of Rolls-Royce colours. Instead,
after some questioning, I found out that I would be travelling on a
small airline, called British Midland, that ran a daily service
between the Derby and Glasgow factories. Far from being in some
interesting plane connected with R-R, I found that our plane was an
old DC3 which had seen better days.I duly got on the plane and was
somewhat nervous flying on my first flight.

@@

>>>>

\begin{figure}[htbp]
   \vspace{2em}
   \centering
   %name of the graphic, without the path AND in EPS format:
   \includegraphics[scale=0.5]{bird_gun.eps}
   %caption of the figure 
   \caption*{\small \em A 1960s chicken gun as used at Hucknall.}
   %label of the figure, which has to correspond to \ref{}:
   \label{fig:birdgun}
\end{figure}

@@

The UK being a small country, everybody went around by train.  As
usual, I was given very little information and told to get myself to
East Midlands airport early on the appointed morning, where a ticket
would be waiting for me. On this occasion I had the good sense to take
my own car to the airport and did not get lost. I expected to find a
plane waiting, painted in some sort of Rolls-Royce colours. Instead,
after some questioning, I found out that I would be travelling on a
small airline, called British Midland, which ran a service, mainly for
R-R personnel, between the Derby East Midlands Airport, near Derby and
Glasgow factories Airport. Far from being in some interesting plane
connected with R-R, I found that our plane was an old DC3 which had
seen better days.I duly got on the plane and was somewhat nervous
flying on my first flight.

@@

In the next article I will describe how I worked hard to climb the
hierarchy at R-R and learnt in an uncomfortable way some lessons on
people management.
